### 2015-11-18 section/1_under.tex
update table 2 and figure 4
revise the heat-map, root-cause table

{\textbf{0*1?}}:
This type of loops only produce results in the last iteration, if any. 
They are often related to search: check a sequence of elements one
by one until the right one is found.
Clearly, whether this type of loops are efficient or not depends on the
workload. If they are indeed inefficient, they are often
fixed by data-structure changes.
As an example, Mozilla JavaScript engine used to store the source-code 
line numbers of all byte-code instructions in a linked list \texttt{script}. 
Later on, many users complained that Mozilla browser freezed when opening
some popular websites. It turned out that those websites contained large
JavaScript files that filled the linked list \texttt{script} with
tens of thousands of nodes. Linear search on \texttt{script} then caused the
to freeze. To fix this problem, 
developers simply replace linked list with hash table
(Mozilla Bug\#347306).
% This improve the performance by 52.60{\bf X}.

@@

\begin{table*}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{|lcccccc|}
\hline
&Apache&Chrome&GCC&Mozilla&MySQL&Total\\
\hline
Total \# of loop bugs & 11 & 4 & 8 & 12 & 10 & 45 \\
\hline
\multicolumn{1}{|l}{ {\bf 0*} Resultness}
&0&0&0&0&0&0\\
\multicolumn{1}{|l}{ {\bf 0*1?} Resultness}
&0&0&0&2&3&5\\
\multicolumn{1}{|l}{{\bf [0$|$1]*} Resultness}
&0&1&1&1&1&4\\
\multicolumn{1}{|l}{{\bf 1*} Resultness}
&1&2&3&6&3&15\\
%&0&2&0&5&0&7&B(4)$|$S(3)\\
%&1&0&3&1&3&8&\\
\hline
\multicolumn{1}{|l}{Cross-{\bf iteration} Redundancy}
&7&1&2&1&1&12\\
\multicolumn{1}{|l}{ Cross-{\bf loop} Redundancy}
&3&0&2&2&2&9\\
  %MySQL15811 is moved from 1* to here; consider it as fixed by M
%\hline
%\multicolumn{8}{|c|}{ \# of {\textit {Other}} bugs}\\
%\multicolumn{1}{|l}{Not in above categories}
\hline
\end{tabular}
}
%\end{adjustwidth}
\caption{Number of bugs in each root-cause category. 
}
\label{tab:root}
\end{table*}

\def\cca#1{\cellcolor{black!#10}\ifnum #1>5\color{white}\fi{#1}}
%For ranges 0-10, multiply by 10 by adding 0 after #1

\begin{table}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{lcccccc}
%\hline
                                 &{\bf 0*}    & {\bf 0*1?} & {\bf [0$|$1]*}   & {\bf 1*} & {\bf C-I}  & {\bf C-L} \\
%\hline
 B                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{4}  & \cca{4}     & \cca{4}   \\
%\hline
 M                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{0}  & \cca{7}     & \cca{5}   \\
 S                               & \cca{0}    & \cca{1}    & \cca{4}          & \cca{4}  & \cca{0}     & \cca{0}   \\
 C                               & \cca{0}    & \cca{4}    & \cca{0}          & \cca{0}  & \cca{0}     & \cca{0}   \\
 O                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{7}  & \cca{1}     & \cca{0}   \\
%\hline

\end{tabular}
}
%\end{adjustwidth}
\caption{Number of bugs fixed by each strategy:
B(atching),  
M(emoization), 
S(kipping the loop),
C(hange the data structure), and O(thers). 
``C-I'': cross- iteration redundancy. 
``C-L'': cross-loop redundancy. 
}
\label{tab:correlation}
\end{table}

@@

\paragraph{Actionability}
As demonstrated in Table \ref{tab:correlation}, 
the root-cause categories in our taxonomy are highly correlated with
fix strategies.
This indicates that our taxonomy is actionable --- once the root cause
is identified, developers roughly know how to fix the problem.
For example, 
almost all 0*1? resultness loops are fixed by data-structure changes;
all [0$|$1]* resultless loops are
fixed by conditionally skipping the loop;
almost all redundant loops are fixed either by 
memoization or batching. 
In fact, as we will discuss later, simple analysis can tell whether 
memoization or batching should be used to fix a redundant loop.
The only problem is that there are no silver bullets for fixing 1* loops.
%all inefficient loops with xx root cause are fixed by xxx.
%xxx

>>>>

{\textbf{0*1?}}:
This type of loops only produce results in the last iteration, if any. 
They are often related to search: check a sequence of elements one
by one until the right one is found.
Clearly, whether this type of loops are efficient or not depends on the
workload. If they are indeed inefficient, they are often
fixed by data-structure changes.
As an example, Mozilla JavaScript engine used to use a linked list 
\texttt{script}
to store debugging information
for every bytecode instruction in a JavaScript file. 
Later on, people complained that Mozilla browsers were very slow in handling
large JavaScript files.
It turned out that those large
JavaScript files filled the linked list \texttt{script} with
tens of thousands of nodes. Repeated search through the
long \texttt{script} list then led to poor performance.
To fix this problem, 
developers simply replace linked list with hash table
(Mozilla Bug\#347306).
% This improve the performance by 52.60{\bf X}.

@@

\comment{
\begin{table*}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{|lcccccc|}
\hline
&Apache&Chrome&GCC&Mozilla&MySQL&Total\\
\hline
Total \# of loop bugs & 11 & 4 & 8 & 12 & 10 & 45 \\
\hline
\multicolumn{1}{|l}{Cross-{\bf iteration} Redundancy}
&7&1&2&1&1&12\\
\multicolumn{1}{|l}{ Cross-{\bf loop} Redundancy}
&3&0&2&2&2&9\\
\multicolumn{1}{|l}{ {\bf 0*} Resultness}
&0&0&0&0&0&0\\
\multicolumn{1}{|l}{ {\bf 0*1?} Resultness}
&0&0&0&2&3&5\\
\multicolumn{1}{|l}{{\bf [0$|$1]*} Resultness}
&0&1&1&1&1&4\\
\multicolumn{1}{|l}{{\bf 1*} Resultness}
&1&2&3&6&3&15\\
%&0&2&0&5&0&7&B(4)$|$S(3)\\
%&1&0&3&1&3&8&\\
  %MySQL15811 is moved from 1* to here; consider it as fixed by M
%\hline
%\multicolumn{8}{|c|}{ \# of {\textit {Other}} bugs}\\
%\multicolumn{1}{|l}{Not in above categories}
\hline
\end{tabular}
}
%\end{adjustwidth}
\caption{Number of bugs in each root-cause category. 
}
\label{tab:root}
\end{table*}
}

\def\cca#1{\cellcolor{black!#10}\ifnum #1>5\color{white}\fi{#1}}

\begin{table*}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{lccccccccccccc}
\hline
                      & Apache &Chrome & GCC  & Mozilla & MySQL &&M$_{\text{emoization}}$  & B$_{\text{atching}}$   &  C & S  & O$_{\text{ther}}$ && Total\\
\cmidrule{2-6}
\cmidrule{8-12}
                      & 11    & 4     & 8    & 12      & 10     && 12  & 12 & 4  & 9  & 8  && 45\\
\hline
\multicolumn{1}{l}{Cross-{\bf iteration} Redundancy}
&7&1&2&1&1&&\cca{7}&\cca{4}&0&0&\cca{1}&&12\\
\multicolumn{1}{l}{ Cross-{\bf loop} Redundancy}
&3&0&2&2&2&&\cca{5}&\cca{4}&\cca{0}&\cca{0}&\cca{0}&&9\\
\multicolumn{1}{l}{ {\bf 0*1?} Resultless}
&0&0&0&2&3&&\cca{0}&\cca{0}&\cca{4}&\cca{1}&\cca{0}&&5\\
\multicolumn{1}{l}{{\bf [0$|$1]*} Resultless}
&0&1&1&1&1&&\cca{0}&\cca{0}&\cca{0}&\cca{4}&\cca{0}&&4\\
\multicolumn{1}{l}{ {\bf 0*} Resultless}
&0&0&0&0&0&&\cca{0}&\cca{0}&\cca{0}&\cca{0}&\cca{0}&&0\\
\multicolumn{1}{l}{{\bf 1*} Resultless}
&1&2&3&6&3&&\cca{0}&\cca{4}&\cca{0}&\cca{4}&\cca{7}&&15\\
  %MySQL15811 is moved from 1* to here; consider it as fixed by M
\hline
\end{tabular}
}
%\end{adjustwidth}
\caption{The distribution among different applications and different fix strategies for bugs with each root-cause category.
(S: conditionally skip the loop; C: change the data structure)
}
\label{tab:root}
\end{table*}

\comment{
\def\cca#1{\cellcolor{black!#10}\ifnum #1>5\color{white}\fi{#1}}
%For ranges 0-10, multiply by 10 by adding 0 after #1
\begin{table}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{lcccccc}
%\hline
                                 &{\bf 0*}    & {\bf 0*1?} & {\bf [0$|$1]*}   & {\bf 1*} & {\bf C-I}  & {\bf C-L} \\
%\hline
 B                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{4}  & \cca{4}     & \cca{4}   \\
%\hline
 M                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{0}  & \cca{7}     & \cca{5}   \\
 S                               & \cca{0}    & \cca{1}    & \cca{4}          & \cca{4}  & \cca{0}     & \cca{0}   \\
 C                               & \cca{0}    & \cca{4}    & \cca{0}          & \cca{0}  & \cca{0}     & \cca{0}   \\
 O                               & \cca{0}    & \cca{0}    & \cca{0}          & \cca{7}  & \cca{1}     & \cca{0}   \\
%\hline

\end{tabular}
}
%\end{adjustwidth}
\caption{Number of bugs fixed by each strategy:
B(atching),  
M(emoization), 
S(kipping the loop),
C(hange the data structure), and O(thers). 
``C-I'': cross- iteration redundancy. 
``C-L'': cross-loop redundancy. 
}
\label{tab:correlation}
\end{table}
}

@@

\paragraph{Actionability}
As demonstrated in Table \ref{tab:correlation}, 
the root-cause categories in our taxonomy are highly correlated with
fix strategies.
This indicates that our taxonomy is actionable --- once the root cause
is identified, developers roughly know how to fix the problem.
For example, 
almost all 0*1? resultless loops are fixed by data-structure changes;
all [0$|$1]* resultless loops are
fixed by conditionally skipping the loop;
almost all redundant loops are fixed either by 
memoization or batching. 
In fact, as we will discuss later, simple analysis can tell whether 
memoization or batching should be used to fix a redundant loop.
The only problem is that there are no silver bullets for fixing 1* loops.
%all inefficient loops with xx root cause are fixed by xxx.
%xxx
